\documentclass[12pt]{book}

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fancyhdr}
\setlength{\headheight}{30pt}


\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-1.4cm}
\setlength{\textheight}{9in}
 \pagestyle{plain}
\pagestyle{fancyplain}
\fancyhf{}
\linespread{1.0}
\lhead{ \fancyplain{}{ABC Player} }
\rhead{ \fancyplain{}{Andrei Ivanov, Olga Shestopalova, Zeke Schmois} }
\rfoot{ \fancyplain{}{\thepage} }

\renewcommand{\arraystretch}{1.5}	
\newcommand{\Ri}{\ \Rightarrow\ }
\newcommand{\Le}{\ \Leftarrow\ }
\newcommand{\Lr}{\ \Leftrightarrow\ }
\newcommand{\ds}{\displaystyle}
\newcommand{\ts}{\textstyle}
\newcommand{\sst}{\scriptstyle}
\newcommand{\sss}{\scriptscriptstyle}
\newcommand{\q}{\quad}
\newcommand{\ap}{\alpha}
\newcommand{\ii}{\^{\i}n }
\newcommand{\si}{\c{s}i }
\newcommand{\oaf}{oricare ar fi }
\newcommand{\nn}{\mathbb{N}}
\newcommand{\ns}{\mathbb{N}^{*}}
\newcommand{\rr}{\mathbb{R}}
\newcommand{\rs}{\mathbb{R}^{*}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\zz}{\mathbb{Z}}
\newcommand{\zs}{\mathbb{Z}^{*}}
\newcommand{\qq}{\mathbb{Q}}
\newcommand{\qs}{\mathbb{Q}^{*}}
\newcommand{\g}{\mathbb{G}}
\newcommand{\di}{\displaystyle}
\newcommand{\ai}{astfel \^{\i}nc\^{a}t }
\newcommand{\la}{\lambda}
\newcommand{\s}{\sigma}
\newcommand{\ri}{\ \rightarrow\ }
\newcommand{\gr}{^{\circ}}
\usepackage{graphicx}


\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%-------1------%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\phantom{xxx}
\bigskip
\centerline{{\large \bf Team Contract}}
\bigskip\bigskip


{\bf Goals} :
\begin{itemize}
\item get an A
\item finish on time
\item procrastinate as little as possible
\end{itemize}

\bigskip
{\bf Personal goals}:
\begin{itemize}
\item We all strive to get As and maybe if there’s time beautify the code, otherwise go for minimum to get an A
\end{itemize}

\bigskip

{\bf Obstacles} :
\begin{itemize}
\item things being harder than expected
\item other classes’ workload and exams
\item sickness/death/relationship problems
\end{itemize}

\bigskip

{\bf  Meeting Norms}:
\begin{itemize}
\item Whenever Andrei is at desk or late at night
\item Preferred to meet in class to get questions answered and will work regardless of meeting place
\item We will definitely be meeting outside of class since we all live in the same building.
\item Since we won’t have any formal meetings, we’ll keep informal notes in a google doc.
\end{itemize}


\bigskip
{\bf Documenting work}:
\begin{itemize}
\item Give real names on commits.
\item Write comments before pushing
\item Keep a google doc alive at all times
\end{itemize}

\bigskip

{\bf Work Norms}:
\begin{itemize}
\item Time allotted to working will be decided based on the amount of work needed to do to reach the next milestone but mostly, we'll be working on the weekends
\item Evenly distributed, modularity
\item  Deadlines will be set as soon as the work is split, taking into consideration the level of difficulty of each section.
\item People with greater strengths in particular areas will be given those parts
\item  Asana used for most of the recording of work tasks
\item If it’s reasonable, make up the work. Otherwise, demand an explanation
\item  Code reviewing will happen as follows: each person will be responsible for reviewing at most one other person’s part.
\item  Difference in opinion of quality of work: try to resolve internally, otherwise ask TA
\item  If someone is slacking, the other teammates will have to make up for it, but this is discouraged
\item  We already agreed on times to meet and work
\end{itemize}


\bigskip
{\bf Coding styles}:
\begin{itemize}
\item  Adhere to Java standards so make sure to Ctrl-Shift-F before pushing things. 
\end{itemize}


\bigskip
{\bf Consensus}:
\begin{itemize}
\item  If one of the three people decides to work less and is satisfied with a B, the other two will take on more responsibilities

\item  Acceptable to have people work more towards the goal

\item  In dire cases, majority will rule

\item  If someone is being stubborn, try to resolve and if not, bring out the wine.
\end{itemize}





\bigskip


\end{document}
  

